### 2014-05-05 abstract.tex
Remove Mosh for now

Working with collaborators at MIT, I have built three systems that
explore an objective-driven, computer-generated approach to protocol
design. My thesis is that making protocols a \emph{function} of stated
assumptions and objectives can improve application performance and
free network technologies to evolve.

@@

This work led to Remy, a tool that programmatically generates
protocols for an uncertain multi-agent network. Remy's
computer-generated algorithms can achieve higher performance and
greater fairness than some sophisticated human-designed schemes,
including ones that put intelligence inside the network. The Remy tool
can then be used to probe open questions of Internet congestion
control---e.g., what is the cost of maintaining backwards
compatibility with existing algorithms? Is there a tradeoff between a
protocol's performance now and its ability to adapt to networks of the
future? How easy is it to ``learn'' a network protocol to achieve
desired goals, given a necessarily imperfect model of the networks
where it ultimately will be deployed?

A third system, Mosh (mobile shell), is a remote-terminal application
and protocol that supports roaming, intermittent connectivity, and
rolling latency compensation. Mosh explicitly models the application
state at the client and server, allowing it to decide at runtime how
to most efficiently keep the client up to date, based on application
objectives and semantics.

>>>>

Working with collaborators at MIT, I have built two systems that
explore an objective-driven, computer-generated approach to protocol
design. My thesis is that making protocols a \emph{function} of stated
assumptions and objectives can improve application performance and
free network technologies to evolve.

@@

This work led to Remy, a tool that programmatically generates
protocols for an uncertain multi-agent network. Remy's
computer-generated algorithms can achieve higher performance and
greater fairness than some sophisticated human-designed schemes,
including ones that put intelligence inside the network.

The Remy tool can then be used to probe open questions of Internet
congestion control---e.g., what is the cost of maintaining backwards
compatibility with existing algorithms? Is there a tradeoff between a
protocol's performance now and its ability to adapt to networks of the
future? How easy is it to ``learn'' a network protocol to achieve
desired goals, given a necessarily imperfect model of the networks
where it ultimately will be deployed?

%A third system, Mosh (mobile shell), is a remote-terminal application
%and protocol that supports roaming, intermittent connectivity, and
%rolling latency compensation. Mosh explicitly models the application
%state at the client and server, allowing it to decide at runtime how
%to most efficiently keep the client up to date, based on application
%objectives and semantics.
